Approximation as Differentiation

### 2025-07-10 main/models.tex
Suggestion to give F a more meaningful name.

\begin{proposition}
  The functor
  $F : \Fam(\LatGal) \to \Fam(\MeetSLat \times \JoinSLat^\op)$ is defined
  on objects as
  $F(X, \partial X) = (X, \lambda x. (\partial X(x), \partial
  X(x)))$. This functor is faithful and preserves coproducts and
  finite products.
\end{proposition}

>>>>

\begin{proposition}
  \label{prop:ho-embedding}
  The functor
  $F : \Fam(\LatGal) \to \Fam(\MeetSLat \times \JoinSLat^\op)$ is defined
  on objects as
  $F(X, \partial X) = (X, \lambda x. (\partial X(x), \partial
  X(x)))$. This functor is faithful and preserves coproducts and
  finite products.
\end{proposition}
